Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-16 paper.tex
new graphs

Firstly, we contacted multiple companies using the Cog VM in production on memory intensive application (>1Gb heaps) and built benchmarks out of their deployed application. As an example, we will discuss in the paper in Section \ref{sec:mooseBench} the Moose benchmarks implemented in collaboration with Feenk\footnote{https://feenk.com/}. Part of the business of Feenk consists in analysing software written in multiple programming languages using the open-source framework Moose~\cite{MoosePaper1,MooseBook1}. Using Moose, the application parses the software to analyse into a model, performs analysis on it and lastly releases the model. This behavior was turned into three benchmarks, growing, accessing and shrinking the heap.

@@

\subsection{Set-up}

To evaluate the performance, we use:
\begin{itemize}
	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
\end{itemize}
We compiled one VMs for Linux with GCC, and one for Mac with LLVM.

\paragraph{Moose benchmark.}The Moose benchmark evaluation was performed on a MacBook pro with Mac OS 10.11.6, a 2.9 Ghz processor Intel Core 5, 8 Gb 1867MHz DDR3 of RAM. The Mac VM was compiled using Apple LLVM version 8.0.0 (clang-800.0.38). The compiled VMs are 64 bits (x64) VMs.

\paragraph{Configurable benchmark.}The Configurable benchmark evaluation was performed on an Asus Zenbook with Ubuntu 16.04 LTS, a 2.2 Ghz processor Intel Core 5, 8 Gb 1600MHz DDR3 of RAM. The Linux VM was compiled using GCC version 5.4.0. The compiled VMs are 32 bits (x86) VMs.

@@

@@

We evaluated the configurable benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by generating specific heap configurations. 
The resulats are shown in Figure \ref{ConfigRes1} and \ref{ConfigRes2}

>>>>

Firstly, we contacted multiple companies using the Cog VM in production on memory intensive application (>1Gb heaps) and built benchmarks out of their deployed application. As an example, we will discuss in the paper in Section \ref{sec:mooseBench} the Moose benchmarks implemented with the help of Feenk\footnote{https://feenk.com/}. Part of the business of Feenk consists in analysing software written in multiple programming languages using the open-source framework Moose~\cite{MoosePaper1,MooseBook1}. Using Moose, the application parses the software to analyse into a model, performs analysis on it and lastly releases the model. Models currently used are encoded in up to 11Gb. This behavior was turned into three benchmarks, growing, accessing and shrinking the heap.

@@

@@

\paragraph{Set-up.}The Moose benchmark evaluation was performed on a MacBook pro with Mac OS 10.11.6, a 2.9 Ghz processor Intel Core 5, 8 Gb 1867MHz DDR3 of RAM. The Mac VM was compiled using Apple LLVM version 8.0.0 (clang-800.0.38). The compiled VMs are 64 bits (x64) VMs.

%To evaluate the performance, we use:
%\begin{itemize}
%	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
%	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
%\end{itemize}

@@

\paragraph{Set-up.}The Configurable benchmark evaluation was performed on an Asus Zenbook with Ubuntu 16.04 LTS, a 2.2 Ghz processor Intel Core 5, 8 Gb 1600MHz DDR3 of RAM. The Linux VM was compiled using GCC version 5.4.0. The compiled VMs are 32 bits (x86) VMs.

We evaluated the configurable benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by generating specific heap configurations. 
The results are shown in Figure \ref{ConfigRes1} and \ref{ConfigRes2}
